LAI Workflow Documentation

### 2021-04-05 LAI.Rmd
typo

    1. For each species, calculated a day of the year average of leaf_fall_LAI (m2/m2), weighted by total trap area of sites observed, to account for differential sampling intensity over time. This gives more weight to dates after 2013 when BCI-50ha site observations began. (Figure \@ref(fig:leaf-fall-LAI))) 
    2. LAI, for the changing fraction on the tree is obtained (Figure \@ref(fig:LAI-ssn-loop)) by   
    looping over days t in 1:365   
    LAI[t] <- sum(leaf_fall_LAI[c(t: (t+sp.lifespan)) %% 365])  
    where sp.lifespan are the number of days in species leaf lifespan  
    To normalise LAI, it is the divided by the maximum value.

>>>>

    1. For each species, calculated a day of the year average of leaf_fall_LAI (m2/m2), weighted by total trap area of sites observed, to account for differential sampling intensity over time. This gives more weight to dates after 2013 when BCI-50ha site observations began. (Figure \@ref(fig:leaf-fall-LAI))) 
    2. LAI, for the changing fraction on the tree is obtained (Figure \@ref(fig:LAI-ssn-loop)) by   
    looping over days t in 1:365   
    LAI[t] <- sum(leaf_fall_LAI[c(t: (t+sp.lifespan)) %% 365])  
    where sp.lifespan are the number of days in species leaf lifespan  
    To normalise LAI, it is then divided by the maximum value.
